---
title: "Count_2011_Run_"
output: 
  html_document:
   code_folding: hide
---

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(plyr)
library(dplyr)
library(tidyr)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
G11<-read_excel("GOC-2011.xlsx")
G11$DATE <- as.Date(G11$DATE, format = "%Y-%m-%d") # Changing to Date format
colnames(G11)[colnames(G11)=="DATE"] <- "Date"
```

```{r}
Dz_11Total<-G11 %>% group_by(Date) %>% summarize(Total_2011_Gen=sum(`TOTAL`),n=n())
Dz_11Goreway<-G11 %>% group_by(Date) %>% summarize(Goreway_2011_Total=sum(`SITHE GOREWAY`),n=n())

Dz_11Halton<-G11 %>% group_by(Date) %>% summarize(Halton_2011_Total=sum(HALTONHILLS),n=n())
Dz_11Portland<-G11 %>% group_by(Date) %>% summarize(Portlands_2011_Total=sum(PORTLANDS),n=n())
Dz_11Greenfeild<-G11 %>% group_by(Date) %>% summarize(GEC_2011_Total=sum(`GREENFIELD ENERGY CENTRE`),n=n())
Dz_11Brighton<-G11 %>% group_by(Date) %>% summarize(Brigton_2011_Total=sum(`BRIGHTON BEACH`),n=n())
Dz_11GB<-cbind(Dz_11Total[,-3],Dz_11Goreway[,2],Dz_11Halton[,2],Dz_11Portland[,2],Dz_11Greenfeild[,2],Dz_11Brighton[,2])
Dz_11Goreway
```

```{r message=FALSE,warning=FALSE}
any(is.na(Dz_11GB))
sum(is.na(Dz_11GB))
colSums(is.na(Dz_11GB)) 
nrow(Dz_11GB)
Dz_11GB<-na.omit(Dz_11GB)
any(is.na(Dz_11GB))
nrow(Dz_11GB)
head(Dz_11GB)
```


### Goreway Power Station
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_11Goreway))
sum(is.na(Dz_11Goreway))
colSums(is.na(Dz_11Goreway)) 
nrow(Dz_11Goreway)
Dz_11Goreway<-na.omit(Dz_11Goreway)
any(is.na(Dz_11Goreway))
nrow(Dz_11Goreway)
head(Dz_11Goreway)
Goreway_U_Status_11<-cut(Dz_11Goreway$Goreway_2011_Total,breaks = c(0,100,50000),labels = c(0,1))
Goreway_U_Status_11<-cbind(Dz_11Goreway,Goreway_U_Status_11)
#Goreway_U_Status_11
any(is.na(Goreway_U_Status_11))


```

```{r}
Goreway_U_Status_11[is.na(Goreway_U_Status_11)]=0
head(Goreway_U_Status_11)
```

```{r}
##aa_G_10<-count(Goreway_U_Status_10,"Goreway_U_Status_10")
aa_G_11<-Goreway_U_Status_11 %>% count(Goreway_U_Status_11)
names(aa_G_11)[1]="Running_Status"
names(aa_G_11)[2]="Goreway_Run"
aa_G_11
```

### Halton Hills Combined Cycle Plant
```{r}

any(is.na(Dz_11Halton))
sum(is.na(Dz_11Halton))
colSums(is.na(Dz_11Halton)) 
nrow(Dz_11Halton)
Dz_11Halton<-na.omit(Dz_11Halton)
any(is.na(Dz_11Halton))
nrow(Dz_11Halton)
head(Dz_11Halton)

Halton_U_Status_11<-cut(Dz_11Halton$Halton_2011_Total,breaks = c(0,100,50000),labels = c(0,1))
Halton_U_Status_11<-cbind(Dz_11Halton,Halton_U_Status_11)
Halton_U_Status_11[is.na(Halton_U_Status_11)]=0
#Halton_U_Status_11

#aa_H_10<-count(Halton_U_Status_10,"Halton_U_Status_10")
aa_H_11<-Halton_U_Status_11 %>% count(Halton_U_Status_11)
names(aa_H_11)[1]="Running_Status"
names(aa_H_11)[2]="Halton_Run"
aa_H_11



```
### Portlands Energy Centre
```{r}
any(is.na(Dz_11Portland))
sum(is.na(Dz_11Portland))
colSums(is.na(Dz_11Portland)) 
nrow(Dz_11Portland)
Dz_11Portland<-na.omit(Dz_11Portland)
any(is.na(Dz_11Portland))
nrow(Dz_11Portland)
head(Dz_11Portland)

Portlands_U_Status_11<-cut(Dz_11Portland$Portlands_2011_Total,breaks = c(0,100,50000),labels = c(0,1))
Portlands_U_Status_11<-cbind(Dz_11Portland,Portlands_U_Status_11)
Portlands_U_Status_11[is.na(Portlands_U_Status_11)]=0
#Portlands_U_Status_11

#aa_P_10<-count(Portlands_U_Status_10,"Portlands_U_Status_10")
aa_P_11<-Portlands_U_Status_11 %>% count(Portlands_U_Status_11)
names(aa_P_11)[1]="Running_Status"
names(aa_P_11)[2]="Portland_Run"
aa_P_11

```
### Greenfield Energy Centre
```{r}
any(is.na(Dz_11Greenfeild))
sum(is.na(Dz_11Greenfeild))
colSums(is.na(Dz_11Greenfeild)) 
nrow(Dz_11Greenfeild)
Dz_11Greenfeild<-na.omit(Dz_11Greenfeild)
any(is.na(Dz_11Greenfeild))
nrow(Dz_11Greenfeild)
head(Dz_11Greenfeild)

Greenfeild_U_Status_11<-cut(Dz_11Greenfeild$GEC_2011_Total,breaks = c(0,100,50000),labels = c(0,1))
Greenfeild_U_Status_11<-cbind(Dz_11Greenfeild,Greenfeild_U_Status_11)
Greenfeild_U_Status_11[is.na(Greenfeild_U_Status_11)]= 0
#Greenfeild_U_Status_11

#aa_GEC_10<-count(Greenfeild_U_Status_10,"Greenfeild_U_Status_10")
aa_GEC_11<-Greenfeild_U_Status_11 %>% count(Greenfeild_U_Status_11)
names(aa_GEC_11)[1]="Running_Status"
names(aa_GEC_11)[2]="Greenfeild_Run"
aa_GEC_11

```

### Brighton Beach Generating Station
```{r}
any(is.na(Dz_11Brighton))
sum(is.na(Dz_11Brighton))
colSums(is.na(Dz_11Brighton)) 
nrow(Dz_11Brighton)
Dz_11Brighton<-na.omit(Dz_11Brighton)
any(is.na(Dz_11Brighton))
nrow(Dz_11Brighton)
head(Dz_11Brighton)

Brighton_U_Status_11<-cut(Dz_11Brighton$Brigton_2011_Total,breaks = c(0,100,50000),labels = c(0,1))
Brighton_U_Status_11<-cbind(Dz_11Brighton,Brighton_U_Status_11)
Brighton_U_Status_11[is.na(Brighton_U_Status_11)]=0
#Brighton_U_Status_11

#aa_BB_10<-count(Brighton_U_Status_10,"Brighton_U_Status_10")
aa_BB_11<-Brighton_U_Status_11 %>% count(Brighton_U_Status_11)
names(aa_BB_11)[1]="Running_Status"
names(aa_BB_11)[2]="Brighton_Run"
aa_BB_11


```


```{r  message=FALSE,warning=FALSE}
U_R_Status_11<-cbind(aa_G_11,aa_H_11[,2],aa_P_11[,2],aa_GEC_11[,2],aa_BB_11[,2])
names(U_R_Status_11)[2]="Goreway"
names(U_R_Status_11)[3]="Halton"
names(U_R_Status_11)[4]="Portlands"
names(U_R_Status_11)[5]="Greenfield"
names(U_R_Status_11)[6]="Brighton"
```
Barplot
```{r}
count<-as.matrix(U_R_Status_11[,-1])
barplot(count)
```

### ggplot
```{r message=FALSE,warning=FALSE}
library(ggplot2)
Plant_Name <-rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brighton"), 2)

No_Run<-c(U_R_Status_11[1,2],U_R_Status_11[1,3],U_R_Status_11[1,4],U_R_Status_11[1,5],U_R_Status_11[1,6])
Run<-c(U_R_Status_11[2,2],U_R_Status_11[2,3],U_R_Status_11[2,4],U_R_Status_11[2,5],U_R_Status_11[2,6])
Days <-c(No_Run, Run)
Run_type <-c(rep("No_Run", 5), rep("Run",5))
mydata <-data.frame(Plant_Name, Days)
mydata

```

```{r}
p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()
```
### Labels to a dodged barplot

```{r}
ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```



