---
title: "Count_2015_Run_"
output: 
  html_document:
   code_folding: hide
---

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(dplyr)
library(tidyr)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
G15<-read_excel("GOC-2015.xlsx")
```

```{r}
G15$Date <- as.Date(G15$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_15Total<-G15 %>% group_by(Date) %>% summarize(Total_2015_Gen=sum(`TOTAL`),n=n())
Dz_15Goreway<-G15 %>% group_by(Date) %>% summarize(Goreway_2015_Total=sum(`SITHE GOREWAY-G11`+
                                  `SITHE GOREWAY-G12`+`SITHE GOREWAY-G13`+`SITHE GOREWAY-G15`),n=n())
Dz_15Halton<-G15 %>% group_by(Date) %>% summarize(Halton_2015_Total=sum(`HALTONHILLS-LT_G1`+`HALTONHILLS-LT_G2`+`HALTONHILLS-LT_G3`),n=n())
Dz_15Portland<-G15 %>% group_by(Date) %>% summarize(Portlands_2015_Total=sum(`PORTLANDS-G1`+`PORTLANDS-G2`+`PORTLANDS-G3`),n=n())
Dz_15Greenfeild<-G15 %>% group_by(Date) %>% summarize(GEC_2015_Total=sum(`GREENFIELD ENERGY CENTRE-G1`+
  `GREENFIELD ENERGY CENTRE-G2`+`GREENFIELD ENERGY CENTRE-G3`+`GREENFIELD ENERGY CENTRE-G4`),n=n())
Dz_15Brighton<-G15 %>% group_by(Date) %>% summarize(Brigton_2015_Total=sum(`BRIGHTON BEACH`),n=n())


head(Dz_15Total)
```

```{r message=FALSE,warning=FALSE}
Dz_15GB<-cbind(Dz_15Total[,-3],Dz_15Goreway[,2],Dz_15Halton[,2],Dz_15Portland[,2],Dz_15Greenfeild[,2],Dz_15Brighton[,2])
head(Dz_15GB)
```
Checking for missing values
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_15GB))
sum(is.na(Dz_15GB))
colSums(is.na(Dz_15GB)) 
nrow(Dz_15GB)
a<-na.omit(Dz_15GB)
any(is.na(a))
```

### Goreway Power Station

```{r message=FALSE,warning=FALSE}
Goreway_U_Status_15<-cut(Dz_15Goreway$Goreway_2015_Total,breaks = c(0,100,10000),labels = c(0,1))
Goreway_U_Status_15<-cbind(Dz_15Goreway,Goreway_U_Status_15)
any(is.na(Goreway_U_Status_15))
```
```{r message=FALSE,warning=FALSE}
Goreway_U_Status_15[is.na(Goreway_U_Status_15)]=0
head(Goreway_U_Status_15)
```
Counting of Running/Notrunning

```{r  message=FALSE,warning=FALSE}
library(plyr)
aa_G_15<-count(Goreway_U_Status_15,"Goreway_U_Status_15")
names(aa_G_15)[1]="Running_Status"
names(aa_G_15)[2]="Goreway_Running_Frequency"
aa_G_15
```

### Halton Hills Combined Cycle Plant
```{r  message=FALSE,warning=FALSE}
Halton_U_Status_15<-cut(Dz_15Halton$Halton_2015_Total,breaks = c(0,100,10000),labels = c(0,1))
Halton_U_Status_15<-cbind(Dz_15Halton,Halton_U_Status_15)
any(is.na(Halton_U_Status_15))
```


```{r  message=FALSE,warning=FALSE}
Halton_U_Status_15[is.na(Halton_U_Status_15)]=0
##head(Halton_U_Status_15)
aa_H_15<-count(Halton_U_Status_15,"Halton_U_Status_15")
names(aa_H_15)[1]="Running_Status"
names(aa_H_15)[2]="Halton_Running_Frequency"
aa_H_15
```
### Portlands Energy Centre
```{r  message=FALSE,warning=FALSE}
Portland_U_Status_15<-cut(Dz_15GB$Portlands_2015_Total,breaks = c(0,100,10000),labels = c(0,1))
Portland_U_Status_15<-cbind(Dz_15Portland,Portland_U_Status_15)
any(is.na(Portland_U_Status_15))
Portland_U_Status_15[is.na(Portland_U_Status_15)]=0
##head(Portland_U_Status_15)
aa_P_15<-count(Portland_U_Status_15,"Portland_U_Status_15")
names(aa_P_15)[1]="Running_Status"
names(aa_P_15)[2]="Portland_U_Status_15"
aa_P_15

```
### Greenfield Energy Centre
```{r  message=FALSE,warning=FALSE}
Greenfield_U_Status_15<-cut(Dz_15GB$GEC_2015_Total,breaks = c(0,100,10000),labels = c(0,1))
Greenfield_U_Status_15<-cbind(Dz_15Greenfeild,Greenfield_U_Status_15)
any(is.na(Greenfield_U_Status_15))
Greenfield_U_Status_15[is.na(Greenfield_U_Status_15)]=0
##head(Greenfield_U_Status_15)
aa_GEC_15<-count(Greenfield_U_Status_15,"Greenfield_U_Status_15")
names(aa_GEC_15)[1]="Running_Status"
names(aa_GEC_15)[2]="Greenfield_U_Status_15"
aa_GEC_15

```
### Brighton Beach Power Station
```{r  message=FALSE,warning=FALSE}
Brigton_Beach_U_Status_15<-cut(Dz_15GB$Brigton_2015_Total,breaks = c(0,100,10000),labels = c(0,1))
Brigton_Beach_U_Status_15<-cbind(Dz_15Brighton,Brigton_Beach_U_Status_15)
any(is.na(Brigton_Beach_U_Status_15))
Brigton_Beach_U_Status_15[is.na(Brigton_Beach_U_Status_15)]=0
```


```{r  message=FALSE,warning=FALSE}
aa_BB_15<-count(Brigton_Beach_U_Status_15,"Brigton_Beach_U_Status_15")
names(aa_BB_15)[1]="Running_Status"
names(aa_BB_15)[2]="Brigton_Beach_U_Status_15"
aa_BB_15

```

```{r  message=FALSE,warning=FALSE}
U_R_Status_15<-cbind(aa_G_15,aa_H_15[,2],aa_P_15[,2],aa_GEC_15[,2],aa_BB_15[,2])
names(U_R_Status_15)[2]="Goreway"
names(U_R_Status_15)[3]="Halton"
names(U_R_Status_15)[4]="Portlands"
names(U_R_Status_15)[5]="Greenfield"
names(U_R_Status_15)[6]="Brigton"
```
Barplot
```{r}
head(U_R_Status_15)
```




```{r  message=FALSE,warning=FALSE}
count<-as.matrix(U_R_Status_15[,-1])
uk<-c("0","1")
barplot(count)
```
### ggplot
```{r warning=FALSE}

library(ggplot2)
Plant_Name <-rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brigton"), 2)

no<-c(U_R_Status_15[1,2],U_R_Status_15[1,3],U_R_Status_15[1,4],U_R_Status_15[1,5],U_R_Status_15[1,6])
yes<-c(U_R_Status_15[2,2],U_R_Status_15[2,3],U_R_Status_15[2,4],U_R_Status_15[2,5],U_R_Status_15[2,6])
Days <-c(no, yes)
Run_type <-c(rep("no", 5), rep("yes",5))
mydata <-data.frame(Plant_Name, Days)
mydata

p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()



```
### Labels to a dodged barplot

```{r}
ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```



