---
title: "Count_2012_Run_"
output: 
  html_document:
   code_folding: hide

---

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(plyr)
library(dplyr)
library(tidyr)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
G12<-read_excel("GOC-2012.xlsx")
G12$DATE <- as.Date(G12$DATE, format = "%Y-%m-%d") # Changing to Date format
colnames(G12)[colnames(G12)=="DATE"] <- "Date"
```

```{r}
##11$Date <- as.Date(G12$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_12Total<-G12 %>% group_by(Date) %>% summarize(Total_2012_Gen=sum(`TOTAL`),n=n())
Dz_12Goreway<-G12 %>% group_by(Date) %>% summarize(Goreway_2012_Total=sum(`SITHE GOREWAY`),n=n())

Dz_12Halton<-G12 %>% group_by(Date) %>% summarize(Halton_2012_Total=sum(HALTONHILLS),n=n())
Dz_12Portland<-G12 %>% group_by(Date) %>% summarize(Portlands_2012_Total=sum(PORTLANDS),n=n())
Dz_12Greenfeild<-G12 %>% group_by(Date) %>% summarize(GEC_2012_Total=sum(`GREENFIELD ENERGY CENTRE`),n=n())
Dz_12Brighton<-G12 %>% group_by(Date) %>% summarize(Brigton_2012_Total=sum(`BRIGHTON BEACH`),n=n())
Dz_12GB<-cbind(Dz_12Total[,-3],Dz_12Goreway[,2],Dz_12Halton[,2],Dz_12Portland[,2],Dz_12Greenfeild[,2],Dz_12Brighton[,2])
Dz_12Goreway
```

```{r message=FALSE,warning=FALSE}
any(is.na(Dz_12GB))
sum(is.na(Dz_12GB))
colSums(is.na(Dz_12GB)) 
nrow(Dz_12GB)
Dz_12GB<-na.omit(Dz_12GB)
any(is.na(Dz_12GB))
nrow(Dz_12GB)
head(Dz_12GB)
```


### Goreway Power Station 
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_12Goreway))
sum(is.na(Dz_12Goreway))
colSums(is.na(Dz_12Goreway)) 
nrow(Dz_12Goreway)
Dz_12Goreway<-na.omit(Dz_12Goreway)
any(is.na(Dz_12Goreway))
nrow(Dz_12Goreway)
head(Dz_12Goreway)
Goreway_U_Status_12<-cut(Dz_12Goreway$Goreway_2012_Total,breaks = c(0,100,50000),labels = c(0,1))
Goreway_U_Status_12<-cbind(Dz_12Goreway,Goreway_U_Status_12)
#Goreway_U_Status_12
any(is.na(Goreway_U_Status_12))


```

```{r}
Goreway_U_Status_12[is.na(Goreway_U_Status_12)]=0
head(Goreway_U_Status_12)
```

```{r}
##aa_G_12<-count(Goreway_U_Status_12,"Goreway_U_Status_12")
aa_G_12<-Goreway_U_Status_12 %>% count(Goreway_U_Status_12)
names(aa_G_12)[1]="Running_Status"
names(aa_G_12)[2]="Goreway_Run"
aa_G_12
```

### Halton Hills Combined Cycle Plant
```{r}

any(is.na(Dz_12Halton))
sum(is.na(Dz_12Halton))
colSums(is.na(Dz_12Halton)) 
nrow(Dz_12Halton)
Dz_12Halton<-na.omit(Dz_12Halton)
any(is.na(Dz_12Halton))
nrow(Dz_12Halton)
head(Dz_12Halton)

Halton_U_Status_12<-cut(Dz_12Halton$Halton_2012_Total,breaks = c(0,100,50000),labels = c(0,1))
Halton_U_Status_12<-cbind(Dz_12Halton,Halton_U_Status_12)
Halton_U_Status_12[is.na(Halton_U_Status_12)]=0
#Halton_U_Status_12

#aa_H_10<-count(Halton_U_Status_10,"Halton_U_Status_10")
aa_H_12<-Halton_U_Status_12 %>% count(Halton_U_Status_12)
names(aa_H_12)[1]="Running_Status"
names(aa_H_12)[2]="Halton_Run"
aa_H_12



```
### Portlands Energy Centre
```{r}
any(is.na(Dz_12Portland))
sum(is.na(Dz_12Portland))
colSums(is.na(Dz_12Portland)) 
nrow(Dz_12Portland)
Dz_12Portland<-na.omit(Dz_12Portland)
any(is.na(Dz_12Portland))
nrow(Dz_12Portland)
head(Dz_12Portland)

Portlands_U_Status_12<-cut(Dz_12Portland$Portlands_2012_Total,breaks = c(0,100,50000),labels = c(0,1))
Portlands_U_Status_12<-cbind(Dz_12Portland,Portlands_U_Status_12)
Portlands_U_Status_12[is.na(Portlands_U_Status_12)]=0
#Portlands_U_Status_12

#aa_P_10<-count(Portlands_U_Status_10,"Portlands_U_Status_10")
aa_P_12<-Portlands_U_Status_12 %>% count(Portlands_U_Status_12)
names(aa_P_12)[1]="Running_Status"
names(aa_P_12)[2]="Portland_Run"
aa_P_12

```
### Greenfield Energy Centre
```{r}
any(is.na(Dz_12Greenfeild))
sum(is.na(Dz_12Greenfeild))
colSums(is.na(Dz_12Greenfeild)) 
nrow(Dz_12Greenfeild)
Dz_12Greenfeild<-na.omit(Dz_12Greenfeild)
any(is.na(Dz_12Greenfeild))
nrow(Dz_12Greenfeild)
head(Dz_12Greenfeild)

Greenfeild_U_Status_12<-cut(Dz_12Greenfeild$GEC_2012_Total,breaks = c(0,100,50000),labels = c(0,1))
Greenfeild_U_Status_12<-cbind(Dz_12Greenfeild,Greenfeild_U_Status_12)
Greenfeild_U_Status_12[is.na(Greenfeild_U_Status_12)]= 0
#Greenfeild_U_Status_12

#aa_GEC_10<-count(Greenfeild_U_Status_10,"Greenfeild_U_Status_10")
aa_GEC_12<-Greenfeild_U_Status_12 %>% count(Greenfeild_U_Status_12)
names(aa_GEC_12)[1]="Running_Status"
names(aa_GEC_12)[2]="Greenfeild_Run"
aa_GEC_12

```

### Brighton Beach Generating Station
```{r}
any(is.na(Dz_12Brighton))
sum(is.na(Dz_12Brighton))
colSums(is.na(Dz_12Brighton)) 
nrow(Dz_12Brighton)
Dz_12Brighton<-na.omit(Dz_12Brighton)
any(is.na(Dz_12Brighton))
nrow(Dz_12Brighton)
head(Dz_12Brighton)

Brighton_U_Status_12<-cut(Dz_12Brighton$Brigton_2012_Total,breaks = c(0,100,50000),labels = c(0,1))
Brighton_U_Status_12<-cbind(Dz_12Brighton,Brighton_U_Status_12)
Brighton_U_Status_12[is.na(Brighton_U_Status_12)]=0
#Brighton_U_Status_12

#aa_BB_10<-count(Brighton_U_Status_10,"Brighton_U_Status_10")
aa_BB_12<-Brighton_U_Status_12 %>% count(Brighton_U_Status_12)
names(aa_BB_12)[1]="Running_Status"
names(aa_BB_12)[2]="Brighton_Run"
aa_BB_12


```


```{r  message=FALSE,warning=FALSE}
U_R_Status_12<-cbind(aa_G_12,aa_H_12[,2],aa_P_12[,2],aa_GEC_12[,2],aa_BB_12[,2])
names(U_R_Status_12)[2]="Goreway"
names(U_R_Status_12)[3]="Halton"
names(U_R_Status_12)[4]="Portlands"
names(U_R_Status_12)[5]="Greenfield"
names(U_R_Status_12)[6]="Brighton"
```
Barplot
```{r}
count<-as.matrix(U_R_Status_12[,-1])
barplot(count)
```





### ggplot
```{r message=FALSE,warning=FALSE}
library(ggplot2)
Plant_Name <-rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brighton"), 2)

No_Run<-c(U_R_Status_12[1,2],U_R_Status_12[1,3],U_R_Status_12[1,4],U_R_Status_12[1,5],U_R_Status_12[1,6])
Run<-c(U_R_Status_12[2,2],U_R_Status_12[2,3],U_R_Status_12[2,4],U_R_Status_12[2,5],U_R_Status_12[2,6])
Days <-c(No_Run, Run)
Run_type <-c(rep("No_Run", 5), rep("Run",5))
mydata <-data.frame(Plant_Name, Days)
mydata


p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()



```
### Labels to a dodged barplot

```{r}
ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```



