---
title: "Count_2013_Run_"
output: 
  html_document:
   code_folding: hide
---

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(plyr)
library(dplyr)
library(tidyr)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
G13<-read_excel("GOC-2013.xlsx")
G13$Date <- as.Date(G13$Date, format = "%Y-%m-%d") # Changing to Date format
#colnames(G13)[colnames(G13)=="DATE"] <- "Date"
```

```{r}
##11$Date <- as.Date(G12$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_13Total<-G13 %>% group_by(Date) %>% summarize(Total_2013_Gen=sum(`TOTAL`),n=n())
Dz_13Goreway<-G13 %>% group_by(Date) %>% summarize(Goreway_2013_Total=sum(`SITHE GOREWAY`),n=n())

Dz_13Halton<-G13 %>% group_by(Date) %>% summarize(Halton_2013_Total=sum(HALTONHILLS),n=n())
Dz_13Portland<-G13 %>% group_by(Date) %>% summarize(Portlands_2013_Total=sum(PORTLANDS),n=n())
Dz_13Greenfeild<-G13 %>% group_by(Date) %>% summarize(GEC_2013_Total=sum(`GREENFIELD ENERGY CENTRE`),n=n())
Dz_13Brighton<-G13 %>% group_by(Date) %>% summarize(Brigton_2013_Total=sum(`BRIGHTON BEACH`),n=n())
Dz_13GB<-cbind(Dz_13Total[,-3],Dz_13Goreway[,2],Dz_13Halton[,2],Dz_13Portland[,2],Dz_13Greenfeild[,2],Dz_13Brighton[,2])
Dz_13Goreway
```

```{r message=FALSE,warning=FALSE}
any(is.na(Dz_13GB))
sum(is.na(Dz_13GB))
colSums(is.na(Dz_13GB)) 
nrow(Dz_13GB)
Dz_13GB<-na.omit(Dz_13GB)
any(is.na(Dz_13GB))
nrow(Dz_13GB)
head(Dz_13GB)
```


### Goreway Power Station
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_13Goreway))
sum(is.na(Dz_13Goreway))
colSums(is.na(Dz_13Goreway)) 
nrow(Dz_13Goreway)
Dz_13Goreway<-na.omit(Dz_13Goreway)
any(is.na(Dz_13Goreway))
nrow(Dz_13Goreway)
head(Dz_13Goreway)
Goreway_U_Status_13<-cut(Dz_13Goreway$Goreway_2013_Total,breaks = c(0,100,50000),labels = c(0,1))
Goreway_U_Status_13<-cbind(Dz_13Goreway,Goreway_U_Status_13)
#Goreway_U_Status_13
any(is.na(Goreway_U_Status_13))


```

```{r}
Goreway_U_Status_13[is.na(Goreway_U_Status_13)]=0
head(Goreway_U_Status_13)
```

```{r}
##aa_G_13<-count(Goreway_U_Status_13,"Goreway_U_Status_13")
aa_G_13<-Goreway_U_Status_13 %>% count(Goreway_U_Status_13)
names(aa_G_13)[1]="Running_Status"
names(aa_G_13)[2]="Goreway_Run"
aa_G_13
```

### Halton Hills Combined Cycle Plant
```{r}

any(is.na(Dz_13Halton))
sum(is.na(Dz_13Halton))
colSums(is.na(Dz_13Halton)) 
nrow(Dz_13Halton)
Dz_13Halton<-na.omit(Dz_13Halton)
any(is.na(Dz_13Halton))
nrow(Dz_13Halton)
head(Dz_13Halton)

Halton_U_Status_13<-cut(Dz_13Halton$Halton_2013_Total,breaks = c(0,100,50000),labels = c(0,1))
Halton_U_Status_13<-cbind(Dz_13Halton,Halton_U_Status_13)
Halton_U_Status_13[is.na(Halton_U_Status_13)]=0
#Halton_U_Status_13

#aa_H_10<-count(Halton_U_Status_10,"Halton_U_Status_10")
aa_H_13<-Halton_U_Status_13 %>% count(Halton_U_Status_13)
names(aa_H_13)[1]="Running_Status"
names(aa_H_13)[2]="Halton_Run"
aa_H_13



```
### Portlands Energy Centre
```{r}
any(is.na(Dz_13Portland))
sum(is.na(Dz_13Portland))
colSums(is.na(Dz_13Portland)) 
nrow(Dz_13Portland)
Dz_13Portland<-na.omit(Dz_13Portland)
any(is.na(Dz_13Portland))
nrow(Dz_13Portland)
head(Dz_13Portland)

Portlands_U_Status_13<-cut(Dz_13Portland$Portlands_2013_Total,breaks = c(0,100,50000),labels = c(0,1))
Portlands_U_Status_13<-cbind(Dz_13Portland,Portlands_U_Status_13)
Portlands_U_Status_13[is.na(Portlands_U_Status_13)]=0
#Portlands_U_Status_13

#aa_P_10<-count(Portlands_U_Status_10,"Portlands_U_Status_10")
aa_P_13<-Portlands_U_Status_13 %>% count(Portlands_U_Status_13)
names(aa_P_13)[1]="Running_Status"
names(aa_P_13)[2]="Portland_Run"
aa_P_13

```
### Greenfield Energy Centre
```{r}
any(is.na(Dz_13Greenfeild))
sum(is.na(Dz_13Greenfeild))
colSums(is.na(Dz_13Greenfeild)) 
nrow(Dz_13Greenfeild)
Dz_13Greenfeild<-na.omit(Dz_13Greenfeild)
any(is.na(Dz_13Greenfeild))
nrow(Dz_13Greenfeild)
head(Dz_13Greenfeild)

Greenfeild_U_Status_13<-cut(Dz_13Greenfeild$GEC_2013_Total,breaks = c(0,100,50000),labels = c(0,1))
Greenfeild_U_Status_13<-cbind(Dz_13Greenfeild,Greenfeild_U_Status_13)
Greenfeild_U_Status_13[is.na(Greenfeild_U_Status_13)]= 0
#Greenfeild_U_Status_13

#aa_GEC_10<-count(Greenfeild_U_Status_10,"Greenfeild_U_Status_10")
aa_GEC_13<-Greenfeild_U_Status_13 %>% count(Greenfeild_U_Status_13)
names(aa_GEC_13)[1]="Running_Status"
names(aa_GEC_13)[2]="Greenfeild_Run"
aa_GEC_13

```

### Brighton Beach Generating Station
```{r}
any(is.na(Dz_13Brighton))
sum(is.na(Dz_13Brighton))
colSums(is.na(Dz_13Brighton)) 
nrow(Dz_13Brighton)
Dz_13Brighton<-na.omit(Dz_13Brighton)
any(is.na(Dz_13Brighton))
nrow(Dz_13Brighton)
head(Dz_13Brighton)

Brighton_U_Status_13<-cut(Dz_13Brighton$Brigton_2013_Total,breaks = c(0,100,50000),labels = c(0,1))
Brighton_U_Status_13<-cbind(Dz_13Brighton,Brighton_U_Status_13)
Brighton_U_Status_13[is.na(Brighton_U_Status_13)]=0
#Brighton_U_Status_13

#aa_BB_10<-count(Brighton_U_Status_10,"Brighton_U_Status_10")
aa_BB_13<-Brighton_U_Status_13 %>% count(Brighton_U_Status_13)
names(aa_BB_13)[1]="Running_Status"
names(aa_BB_13)[2]="Brighton_Run"
aa_BB_13


```


```{r  message=FALSE,warning=FALSE}
U_R_Status_13<-cbind(aa_G_13,aa_H_13[,2],aa_P_13[,2],aa_GEC_13[,2],aa_BB_13[,2])
names(U_R_Status_13)[2]="Goreway"
names(U_R_Status_13)[3]="Halton"
names(U_R_Status_13)[4]="Portlands"
names(U_R_Status_13)[5]="Greenfield"
names(U_R_Status_13)[6]="Brighton"
```
Barplot
```{r}
count<-as.matrix(U_R_Status_13[,-1])
barplot(count)
```





### ggplot
```{r message=FALSE,warning=FALSE}
library(ggplot2)
Plant_Name <-rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brighton"), 2)

No_Run<-c(U_R_Status_13[1,2],U_R_Status_13[1,3],U_R_Status_13[1,4],U_R_Status_13[1,5],U_R_Status_13[1,6])
Run<-c(U_R_Status_13[2,2],U_R_Status_13[2,3],U_R_Status_13[2,4],U_R_Status_13[2,5],U_R_Status_13[2,6])
Days <-c(No_Run, Run)
Run_type <-c(rep("No_Run", 5), rep("Run",5))
mydata <-data.frame(Plant_Name, Days)
mydata

p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()

```

### Labels to a dodged barplot

```{r}
ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```


