---
title: "Count_2016_Run_"
output: 
  html_document:
   code_folding: hide
---

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(dplyr)
library(tidyr)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
#G16<-read_excel("Output/GOC-2016.xlsx")
G16<-read_excel("GOC-2016.xlsx")
```

```{r}
G16$Date <- as.Date(G16$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_16Total<-G16 %>% group_by(Date) %>% summarize(Total_2016_Gen=sum(`TOTAL`),n=n())
Dz_16Goreway<-G16 %>% group_by(Date) %>% summarize(Goreway_2016_Total=sum(`SITHE GOREWAY-G11`+
                                  `SITHE GOREWAY-G12`+`SITHE GOREWAY-G13`+`SITHE GOREWAY-G15`),n=n())
Dz_16Halton<-G16 %>% group_by(Date) %>% summarize(Halton_2016_Total=sum(`HALTONHILLS-LT_G1`+`HALTONHILLS-LT_G2`+`HALTONHILLS-LT_G3`),n=n())
Dz_16Portland<-G16 %>% group_by(Date) %>% summarize(Portlands_2016_Total=sum(`PORTLANDS-G1`+`PORTLANDS-G2`+`PORTLANDS-G3`),n=n())
Dz_16Greenfeild<-G16 %>% group_by(Date) %>% summarize(GEC_2016_Total=sum(`GREENFIELD ENERGY CENTRE-G1`+
  `GREENFIELD ENERGY CENTRE-G2`+`GREENFIELD ENERGY CENTRE-G3`+`GREENFIELD ENERGY CENTRE-G4`),n=n())
Dz_16Brighton<-G16 %>% group_by(Date) %>% summarize(Brigton_2016_Total=sum(`BRIGHTON BEACH`),n=n())


head(Dz_16Total)
```

```{r message=FALSE,warning=FALSE}
Dz_16GB<-cbind(Dz_16Total[,-3],Dz_16Goreway[,2],Dz_16Halton[,2],Dz_16Portland[,2],Dz_16Greenfeild[,2],Dz_16Brighton[,2])
head(Dz_16GB)
```
Checking for missing values
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_16GB))
sum(is.na(Dz_16GB))
colSums(is.na(Dz_16GB)) 
nrow(Dz_16GB)
a<-na.omit(Dz_16GB)
any(is.na(a))
```

### Goreway Power Station

```{r message=FALSE,warning=FALSE}
Goreway_U_Status_16<-cut(Dz_16Goreway$Goreway_2016_Total,breaks = c(0,100,10000),labels = c(0,1))
Goreway_U_Status_16<-cbind(Dz_16Goreway,Goreway_U_Status_16)
any(is.na(Goreway_U_Status_16))
```
```{r message=FALSE,warning=FALSE}
Goreway_U_Status_16[is.na(Goreway_U_Status_16)]=0
head(Goreway_U_Status_16)
```
Counting of Running/Notrunning

```{r  message=FALSE,warning=FALSE}
library(plyr)
aa_G_16<-count(Goreway_U_Status_16,"Goreway_U_Status_16")
names(aa_G_16)[1]="Running_Status"
names(aa_G_16)[2]="Goreway_Running_Frequency"
aa_G_16
```

### Halton Hills Combined Cycle Plant
```{r  message=FALSE,warning=FALSE}
Halton_U_Status_16<-cut(Dz_16Halton$Halton_2016_Total,breaks = c(0,100,10000),labels = c(0,1))
Halton_U_Status_16<-cbind(Dz_16Halton,Halton_U_Status_16)
any(is.na(Halton_U_Status_16))
```


```{r  message=FALSE,warning=FALSE}
Halton_U_Status_16[is.na(Halton_U_Status_16)]=0
##head(Halton_U_Status_18)
aa_H_16<-count(Halton_U_Status_16,"Halton_U_Status_16")
names(aa_H_16)[1]="Running_Status"
names(aa_H_16)[2]="Halton_Running_Frequency"
aa_H_16
```
### Portlands Energy Centre
```{r  message=FALSE,warning=FALSE}
Portland_U_Status_16<-cut(Dz_16GB$Portlands_2016_Total,breaks = c(0,100,10000),labels = c(0,1))
Portland_U_Status_16<-cbind(Dz_16Portland,Portland_U_Status_16)
any(is.na(Portland_U_Status_16))
Portland_U_Status_16[is.na(Portland_U_Status_16)]=0
##head(Portland_U_Status_16)
aa_P_16<-count(Portland_U_Status_16,"Portland_U_Status_16")
names(aa_P_16)[1]="Running_Status"
names(aa_P_16)[2]="Portland_U_Status_16"
aa_P_16

```
### Greenfield Energy Centre
```{r  message=FALSE,warning=FALSE}
Greenfield_U_Status_16<-cut(Dz_16GB$GEC_2016_Total,breaks = c(0,100,10000),labels = c(0,1))
Greenfield_U_Status_16<-cbind(Dz_16Greenfeild,Greenfield_U_Status_16)
any(is.na(Greenfield_U_Status_16))
Greenfield_U_Status_16[is.na(Greenfield_U_Status_16)]=0
##head(Greenfield_U_Status_16)
aa_GEC_16<-count(Greenfield_U_Status_16,"Greenfield_U_Status_16")
names(aa_GEC_16)[1]="Running_Status"
names(aa_GEC_16)[2]="Greenfield_U_Status_16"
aa_GEC_16

```
### Brighton Beach Power Station
```{r  message=FALSE,warning=FALSE}
Brigton_Beach_U_Status_16<-cut(Dz_16GB$Brigton_2016_Total,breaks = c(0,100,10000),labels = c(0,1))
Brigton_Beach_U_Status_16<-cbind(Dz_16Brighton,Brigton_Beach_U_Status_16)
any(is.na(Brigton_Beach_U_Status_16))
Brigton_Beach_U_Status_16[is.na(Brigton_Beach_U_Status_16)]=0
```


```{r  message=FALSE,warning=FALSE}
aa_BB_16<-count(Brigton_Beach_U_Status_16,"Brigton_Beach_U_Status_16")
names(aa_BB_16)[1]="Running_Status"
names(aa_BB_16)[2]="Brigton_Beach_U_Status_16"
aa_BB_16

```

```{r  message=FALSE,warning=FALSE}
U_R_Status_16<-cbind(aa_G_16,aa_H_16[,2],aa_P_16[,2],aa_GEC_16[,2],aa_BB_16[,2])
names(U_R_Status_16)[2]="Goreway"
names(U_R_Status_16)[3]="Halton"
names(U_R_Status_16)[4]="Portlands"
names(U_R_Status_16)[5]="Greenfield"
names(U_R_Status_16)[6]="Brigton"
```
Barplot
```{r}
head(U_R_Status_16)
```




```{r  message=FALSE,warning=FALSE}
count<-as.matrix(U_R_Status_16[,-1])
uk<-c("0","1")
barplot(count)
```
ggplot
```{r warning=FALSE}

library(ggplot2)
Plant_Name <-rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brigton"), 2)

no<-c(U_R_Status_16[1,2],U_R_Status_16[1,3],U_R_Status_16[1,4],U_R_Status_16[1,5],U_R_Status_16[1,6])
yes<-c(U_R_Status_16[2,2],U_R_Status_16[2,3],U_R_Status_16[2,4],U_R_Status_16[2,5],U_R_Status_16[2,6])
Days <-c(no, yes)
Run_type <-c(rep("no", 5), rep("yes",5))
mydata <-data.frame(Plant_Name, Days)
mydata


p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()



```

### Labels to a dodged barplot

```{r}
ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()

```


