---
title: "Count_2010_Run_"
output: 
  html_document:
   code_folding: hide

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
G10<-read_excel("GOC-2010.xlsx")
G10$DATE <- as.Date(G10$DATE, format = "%Y-%m-%d") # Changing to Date format
colnames(G10)[colnames(G10)=="DATE"] <- "Date"
```

```{r}
##11$Date <- as.Date(G12$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_10Total<-G10 %>% group_by(Date) %>% summarize(Total_2010_Gen=sum(`TOTAL`),n=n())
Dz_10Goreway<-G10 %>% group_by(Date) %>% summarize(Goreway_2010_Total=sum(`SITHE GOREWAY`),n=n())

Dz_10Halton<-G10 %>% group_by(Date) %>% summarize(Halton_2010_Total=sum(HALTONHILLS),n=n())
Dz_10Portland<-G10 %>% group_by(Date) %>% summarize(Portlands_2010_Total=sum(PORTLANDS),n=n())
Dz_10Greenfeild<-G10 %>% group_by(Date) %>% summarize(GEC_2010_Total=sum(`GREENFIELD ENERGY CENTRE`),n=n())
Dz_10Brighton<-G10 %>% group_by(Date) %>% summarize(Brigton_2010_Total=sum(`BRIGHTON BEACH`),n=n())
Dz_10GB<-cbind(Dz_10Total[,-3],Dz_10Goreway[,2],Dz_10Halton[,2],Dz_10Portland[,2],Dz_10Greenfeild[,2],Dz_10Brighton[,2])
Dz_10Goreway
```

```{r message=FALSE,warning=FALSE}
any(is.na(Dz_10GB))
sum(is.na(Dz_10GB))
colSums(is.na(Dz_10GB)) 
nrow(Dz_10GB)
Dz_10GB<-na.omit(Dz_10GB)
any(is.na(Dz_10GB))
nrow(Dz_10GB)
head(Dz_10GB)
```


## Goreway Power Station
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_10Goreway))
sum(is.na(Dz_10Goreway))
colSums(is.na(Dz_10Goreway)) 
nrow(Dz_10Goreway)
Dz_10Goreway<-na.omit(Dz_10Goreway)
any(is.na(Dz_10Goreway))
nrow(Dz_10Goreway)
head(Dz_10Goreway)
Goreway_U_Status_10<-cut(Dz_10Goreway$Goreway_2010_Total,breaks = c(0,100,50000),labels = c(0,1))
Goreway_U_Status_10<-cbind(Dz_10Goreway,Goreway_U_Status_10)
#Goreway_U_Status_10
any(is.na(Goreway_U_Status_10))


```

```{r}
Goreway_U_Status_10[is.na(Goreway_U_Status_10)]=0
head(Goreway_U_Status_10)
```

```{r}
##aa_G_10<-count(Goreway_U_Status_10,"Goreway_U_Status_10")
aa_G_10<-Goreway_U_Status_10 %>% count(Goreway_U_Status_10)
names(aa_G_10)[1]="Running_Status"
names(aa_G_10)[2]="Goreway_Run"
aa_G_10
```

## Halton Hills Generating Station
```{r}

any(is.na(Dz_10Halton))
sum(is.na(Dz_10Halton))
colSums(is.na(Dz_10Halton)) 
nrow(Dz_10Halton)
Dz_10Halton<-na.omit(Dz_10Halton)
any(is.na(Dz_10Halton))
nrow(Dz_10Halton)
head(Dz_10Halton)

Halton_U_Status_10<-cut(Dz_10Halton$Halton_2010_Total,breaks = c(0,100,50000),labels = c(0,1))
Halton_U_Status_10<-cbind(Dz_10Halton,Halton_U_Status_10)
Halton_U_Status_10[is.na(Halton_U_Status_10)]=0
#Halton_U_Status_10

#aa_H_10<-count(Halton_U_Status_10,"Halton_U_Status_10")
aa_H_10<-Halton_U_Status_10 %>% count(Halton_U_Status_10)
names(aa_H_10)[1]="Running_Status"
names(aa_H_10)[2]="Halton_Run"
aa_H_10



```
## Portlands Energy Centre
```{r}
any(is.na(Dz_10Portland))
sum(is.na(Dz_10Portland))
colSums(is.na(Dz_10Portland)) 
nrow(Dz_10Portland)
Dz_10Portland<-na.omit(Dz_10Portland)
any(is.na(Dz_10Portland))
nrow(Dz_10Portland)
head(Dz_10Portland)

Portlands_U_Status_10<-cut(Dz_10Portland$Portlands_2010_Total,breaks = c(0,100,50000),labels = c(0,1))
Portlands_U_Status_10<-cbind(Dz_10Portland,Portlands_U_Status_10)
Portlands_U_Status_10[is.na(Portlands_U_Status_10)]=0
#Portlands_U_Status_10

#aa_P_10<-count(Portlands_U_Status_10,"Portlands_U_Status_10")
aa_P_10<-Portlands_U_Status_10 %>% count(Portlands_U_Status_10)
names(aa_P_10)[1]="Running_Status"
names(aa_P_10)[2]="Portland_Run"
aa_P_10

```
## Greenfield Energy Centre
```{r}
any(is.na(Dz_10Greenfeild))
sum(is.na(Dz_10Greenfeild))
colSums(is.na(Dz_10Greenfeild)) 
nrow(Dz_10Greenfeild)
Dz_10Greenfeild<-na.omit(Dz_10Greenfeild)
any(is.na(Dz_10Greenfeild))
nrow(Dz_10Greenfeild)
head(Dz_10Greenfeild)

Greenfeild_U_Status_10<-cut(Dz_10Greenfeild$GEC_2010_Total,breaks = c(0,100,50000),labels = c(0,1))
Greenfeild_U_Status_10<-cbind(Dz_10Greenfeild,Greenfeild_U_Status_10)
Greenfeild_U_Status_10[is.na(Greenfeild_U_Status_10)]= 0
#Greenfeild_U_Status_10

#aa_GEC_10<-count(Greenfeild_U_Status_10,"Greenfeild_U_Status_10")
aa_GEC_10<-Greenfeild_U_Status_10 %>% count(Greenfeild_U_Status_10)
names(aa_GEC_10)[1]="Running_Status"
names(aa_GEC_10)[2]="Greenfeild_Run"
aa_GEC_10

```

## Brighton Beach Power Station
```{r}
any(is.na(Dz_10Brighton))
sum(is.na(Dz_10Brighton))
colSums(is.na(Dz_10Brighton)) 
nrow(Dz_10Brighton)
Dz_10Brighton<-na.omit(Dz_10Brighton)
any(is.na(Dz_10Brighton))
nrow(Dz_10Brighton)
head(Dz_10Brighton)

Brighton_U_Status_10<-cut(Dz_10Brighton$Brigton_2010_Total,breaks = c(0,100,50000),labels = c(0,1))
Brighton_U_Status_10<-cbind(Dz_10Brighton,Brighton_U_Status_10)
Brighton_U_Status_10[is.na(Brighton_U_Status_10)]=0
#Brighton_U_Status_10

#aa_BB_10<-count(Brighton_U_Status_10,"Brighton_U_Status_10")
aa_BB_10<-Brighton_U_Status_10 %>% count(Brighton_U_Status_10)
names(aa_BB_10)[1]="Running_Status"
names(aa_BB_10)[2]="Brighton_Run"
aa_BB_10


```

```{r  message=FALSE,warning=FALSE}
U_R_Status_10<-cbind(aa_G_10,aa_H_10[,2],aa_P_10[,2],aa_GEC_10[,2],aa_BB_10[,2])
names(U_R_Status_10)[2]="Goreway"
names(U_R_Status_10)[3]="Halton"
names(U_R_Status_10)[4]="Portlands"
names(U_R_Status_10)[5]="Greenfield"
names(U_R_Status_10)[6]="Brigton"
```
Barplot
```{r}
count<-as.matrix(U_R_Status_10[,-1])
barplot(count)
```
##ggplot

```{r message=FALSE,warning=FALSE}
Plant_Name <- rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brighton"), 2)
No_Run <-c(U_R_Status_10[1,2],U_R_Status_10[1,3],U_R_Status_10[1,4],U_R_Status_10[1,5],U_R_Status_10[1,6])
Run<-c(U_R_Status_10[2,2],U_R_Status_10[2,3],U_R_Status_10[2,4],U_R_Status_10[2,5],U_R_Status_10[2,6])
Days <-c(No_Run, Run)
Run_type <-c(rep("No_Run", 5), rep("Run",5))
mydata <-data.frame(Plant_Name, Days)
mydata
```


```{r}
p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()
```

### Labels to a dodged barplot
```{r}

ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```













