---
title: "Count_2014_Run_"
output: 
  html_document:
   code_folding: hide
---

```{r message=FALSE,warning=FALSE}
library(readxl)
library(lubridate)
library(dplyr)
library(tidyr)
```
Natural gas combine cycle plant generation depends upon market demand . Attemp has been made to calculate the number of days plant was supplying power to grid.It is a first attempt for a comparitive study with counting wind generating days
```{r echo=TRUE}
G14<-read_excel("GOC-2014.xlsx")
```

```{r}
G14$Date <- as.Date(G14$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_14Total<-G14 %>% group_by(Date) %>% summarize(Total_2014_Gen=sum(`TOTAL`),n=n())
Dz_14Goreway<-G14 %>% group_by(Date) %>% summarize(Goreway_2014_Total=sum(`SITHE GOREWAY`),n=n())
Dz_14Halton<-G14 %>% group_by(Date) %>% summarize(Halton_2014_Total=sum(HALTONHILLS),n=n())
Dz_14Portland<-G14 %>% group_by(Date) %>% summarize(Portlands_2014_Total=sum(PORTLANDS),n=n())
Dz_14Greenfeild<-G14 %>% group_by(Date) %>% summarize(GEC_2014_Total=sum(`GREENFIELD ENERGY CENTRE`),n=n())
Dz_14Brighton<-G14 %>% group_by(Date) %>% summarize(Brigton_2014_Total=sum(`BRIGHTON BEACH`),n=n())


head(Dz_14Total)
```

```{r message=FALSE,warning=FALSE}
Dz_14GB<-cbind(Dz_14Total[,-3],Dz_14Goreway[,2],Dz_14Halton[,2],Dz_14Portland[,2],Dz_14Greenfeild[,2],Dz_14Brighton[,2])
head(Dz_14GB)
```
Checking for missing values
```{r message=FALSE,warning=FALSE}
any(is.na(Dz_14GB))
sum(is.na(Dz_14GB))
colSums(is.na(Dz_14GB)) 
nrow(Dz_14GB)
a<-na.omit(Dz_14GB)
any(is.na(a))
```

### Goreway Power Station

```{r message=FALSE,warning=FALSE}
Goreway_U_Status_14<-cut(Dz_14Goreway$Goreway_2014_Total,breaks = c(0,100,10000),labels = c(0,1))
Goreway_U_Status_14<-cbind(Dz_14Goreway,Goreway_U_Status_14)
any(is.na(Goreway_U_Status_14))
```
```{r message=FALSE,warning=FALSE}
Goreway_U_Status_14[is.na(Goreway_U_Status_14)]=0
head(Goreway_U_Status_14)
```
Counting of Running/Notrunning

```{r  message=FALSE,warning=FALSE}
library(plyr)
aa_G_14<-count(Goreway_U_Status_14,"Goreway_U_Status_14")
names(aa_G_14)[1]="Running_Status"
names(aa_G_14)[2]="Goreway_Running_Frequency"
aa_G_14
```

### Halton Hills Combined Cycle Plant
```{r  message=FALSE,warning=FALSE}
Halton_U_Status_14<-cut(Dz_14Halton$Halton_2014_Total,breaks = c(0,100,10000),labels = c(0,1))
Halton_U_Status_14<-cbind(Dz_14Halton,Halton_U_Status_14)
any(is.na(Halton_U_Status_14))
```


```{r  message=FALSE,warning=FALSE}
Halton_U_Status_14[is.na(Halton_U_Status_14)]=0
##head(Halton_U_Status_14)4
aa_H_14<-count(Halton_U_Status_14,"Halton_U_Status_14")
names(aa_H_14)[1]="Running_Status"
names(aa_H_14)[2]="Halton_Running_Frequency"
aa_H_14
```
### Portlands Energy Centre
```{r  message=FALSE,warning=FALSE}
Portland_U_Status_14<-cut(Dz_14GB$Portlands_2014_Total,breaks = c(0,100,10000),labels = c(0,1))
Portland_U_Status_14<-cbind(Dz_14Portland,Portland_U_Status_14)
any(is.na(Portland_U_Status_14))
Portland_U_Status_14[is.na(Portland_U_Status_14)]=0
##head(Portland_U_Status_14)
aa_P_14<-count(Portland_U_Status_14,"Portland_U_Status_14")
names(aa_P_14)[1]="Running_Status"
names(aa_P_14)[2]="Portland_U_Status_14"
aa_P_14

```
### Greenfield Energy Centre
```{r  message=FALSE,warning=FALSE}
Greenfield_U_Status_14<-cut(Dz_14GB$GEC_2014_Total,breaks = c(0,100,10000),labels = c(0,1))
Greenfield_U_Status_14<-cbind(Dz_14Greenfeild,Greenfield_U_Status_14)
any(is.na(Greenfield_U_Status_14))
Greenfield_U_Status_14[is.na(Greenfield_U_Status_14)]=0
##head(Greenfield_U_Status_14)
aa_GEC_14<-count(Greenfield_U_Status_14,"Greenfield_U_Status_14")
names(aa_GEC_14)[1]="Running_Status"
names(aa_GEC_14)[2]="Greenfield_U_Status_14"
aa_GEC_14

```
### Brighton Beach Generating Station
```{r  message=FALSE,warning=FALSE}
Brigton_Beach_U_Status_14<-cut(Dz_14GB$Brigton_2014_Total,breaks = c(0,100,10000),labels = c(0,1))
Brigton_Beach_U_Status_14<-cbind(Dz_14Brighton,Brigton_Beach_U_Status_14)
any(is.na(Brigton_Beach_U_Status_14))
Brigton_Beach_U_Status_14[is.na(Brigton_Beach_U_Status_14)]=0
```


```{r  message=FALSE,warning=FALSE}
aa_BB_14<-count(Brigton_Beach_U_Status_14,"Brigton_Beach_U_Status_14")
names(aa_BB_14)[1]="Running_Status"
names(aa_BB_14)[2]="Brigton_Beach_U_Status_14"
aa_BB_14

```

```{r  message=FALSE,warning=FALSE}
U_R_Status_14<-cbind(aa_G_14,aa_H_14[,2],aa_P_14[,2],aa_GEC_14[,2],aa_BB_14[,2])
names(U_R_Status_14)[2]="Goreway"
names(U_R_Status_14)[3]="Halton"
names(U_R_Status_14)[4]="Portlands"
names(U_R_Status_14)[5]="Greenfield"
names(U_R_Status_14)[6]="Brigton"
```
Barplot
```{r}
head(U_R_Status_14)
```




```{r  message=FALSE,warning=FALSE}
count<-as.matrix(U_R_Status_14[,-1])
uk<-c("0","1")
barplot(count)
```
### ggplot
```{r warning=FALSE}

library(ggplot2)
Plant_Name <-rep(c("Goreway", "Halton", "Portlands", "Greenfield", "Brigton"), 2)

no<-c(U_R_Status_14[1,2],U_R_Status_14[1,3],U_R_Status_14[1,4],U_R_Status_14[1,5],U_R_Status_14[1,6])
yes<-c(U_R_Status_14[2,2],U_R_Status_14[2,3],U_R_Status_14[2,4],U_R_Status_14[2,5],U_R_Status_14[2,6])
Days <-c(no, yes)
Run_type <-c(rep("no", 5), rep("yes",5))
mydata <-data.frame(Plant_Name, Days)
mydata


p <-ggplot(mydata, aes(Plant_Name, Days))
p +geom_bar(stat= "identity",aes(fill=Run_type),position="dodge")+xlab("Plants Name")+ylab("Number of Days")+theme_bw()



```
### Labels to a dodged barplot

```{r}
ggplot(data=mydata, aes(x=Plant_Name, y=Days, fill=Run_type)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(label=Days), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired")+
  theme_minimal()
```



