---
title: "Generation Of Goreway Power Station from the year 2010 - 2018"
output: 
  html_document:
   code_folding: hide

---

### Generation data downloaded from IESO site ( http://www.ieso.ca/en/Power-Data/Data-Directory)

```{r message = FALSE,warning=FALSE}
library(rlang)
library(tidyverse)
library(lubridate)
library(zoo)
library(readxl)
```

```{r}
G10<-read_excel("GOC-2010.xlsx")
head(G10,n=5) # Head gives the first five rows of the data . Its gives generating units available .
```

```{r}
#tail(G10,5) # Tail gives last five rows can be useful when data from external source
```
```{r}
#str(G10) # Str() tells how many rows (observations in statistical R ) and columns ( variables R ) it contains, along with type of data gives 
```
```{r}
#summary(G10$`SITHE GOREWAY`) # summary function gets the statistical summary of the dataset by just running on either a column or the complete dataset
```

```{r message = FALSE,warning=FALSE}
class(G10) # gives class/ data type of argument
```

```{r message = FALSE,warning=FALSE}
dim(G10) # Dimensions of the data set 
```

```{r}
#is.na(G10)
```
```{r message = FALSE,warning=FALSE}
table(is.na(G10)) # Gives total number of missing values 
```
```{r}
#colSums(is.na(G10)) # checking variables in which missing values are present
```

```{r message = FALSE,warning=FALSE}
sum(is.na(G10$`SITHE GOREWAY`)) # shows number of missing values in `SITHE GOREWAY` 
```

```{r }
mean(G10$`SITHE GOREWAY`) # Missing values hinders in calculation in a dataset. As only one missing values we try to calculate mean                                                                                                                              generation 

mean(G10$`SITHE GOREWAY`,na.rm=TRUE) # TRUE ignores the missing values whereas .omit removes the missing values 
```

```{r}
summary(G10$`SITHE GOREWAY`,na.rm=TRUE)
```
## Analysis of the data columns
### 1. Date needs to be changed to Date format .

```{r}
G10$DATE <- as.Date(G10$DATE, format = "%Y-%m-%d") # Changing to Date format
```

### 2. As the given data is in hourly we are grouping hourly into daily . 
###    Total daily generation gives a broad picture of the data . Here we considering Sithe Goreway ( Goreway Power Station ) for study purpose.

```{r}
Dz_10<-G10 %>% group_by(DATE) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
head(Dz_10) 
```
```{r message = FALSE,warning=FALSE}
#library(ggplot2)
#plot<-ggplot(Dz_10, aes(x=~Date,y=~Goreway_Total)) + geom_line()
#plot
```

```{r message = FALSE,warning=FALSE}
#library(plotly)
#plot_ly(Dz_10, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines+markers')
#plot_ly(Dz_10, x=~DATE) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2010')
```

### Similarly grouping hourly MW to daily was performed from the year 2011 to 2018
### Year 2011

```{r}
G11<-read_excel("GOC-2011.xlsx")
G11$DATE <- as.Date(G11$DATE, format = "%Y-%m-%d") # Changing to Date format
Dz_11<-G11 %>% group_by(DATE) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
head(Dz_11)
```
##plot_ly(Dz_11, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines+markers')
```{r}
#plot_ly(Dz_11, x=~DATE) %>% add_trace(y=~Goreway_Total, mode='lines') %>% layout(title='Goreway Generation 2011')

```




### Year 2012
```{r}
G12<-read_excel("GOC-2012.xlsx")
G12$DATE <- as.Date(G12$DATE, format = "%Y-%m-%d") # Changing to Date format
Dz_12<-G12 %>% group_by(DATE) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
head(Dz_12)
```

```{r}
#plot_ly(Dz_12, x=~DATE) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2012')
```

### Year 2013

```{r}
G13<-read_excel("GOC-2013.xlsx")
G13$Date <- as.Date(G13$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_13<-G13 %>% group_by(Date) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
head(Dz_13)
```

```{r}
#plot_ly(Dz_13, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2013')
```

### Year 2014

```{r}
G14<-read_excel("GOC-2014.xlsx")
G14$Date <- as.Date(G14$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_14<-G14 %>% group_by(Date) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
head(Dz_14)
```

```{r}
#plot_ly(Dz_14, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2014')
```
### Year 2015

```{r}
G15<-read_excel("GOC-2015.xlsx")
G15$Date <- as.Date(G15$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_15<-G15 %>% group_by(Date) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY-G11`+`SITHE GOREWAY-G12`+`SITHE GOREWAY-G13`+`SITHE GOREWAY-G15`),n=n())
head(Dz_15)
```

```{r}
#plot_ly(Dz_15, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2015')
```
### Year 2016

```{r}
G16<-read_excel("GOC-2016.xlsx")
G16$Date <- as.Date(G16$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_16<-G16 %>% group_by(Date) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY-G11`+`SITHE GOREWAY-G12`+`SITHE GOREWAY-G13`+`SITHE GOREWAY-G15`),n=n())
head(Dz_16)

```

```{r}
#plot_ly(Dz_16, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2016')
```

### Year 2017
```{r}
G17<-read_excel("GOC-2017.xlsx")
G17$Date <- as.Date(G17$Date, format = "%Y-%m-%d") # Changing to Date format
Dz_17<-G17 %>% group_by(Date) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY-G11`+`SITHE GOREWAY-G12`+`SITHE GOREWAY-G13`+`SITHE GOREWAY-G15`),n=n())
head(Dz_17)
```

```{r}
#plot_ly(Dz_17, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2017')
```

### Year 2018

```{r}
G18<-read_excel("GOC-2018.xlsx")
Dz_18<-G18 %>% group_by(Date) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY-G11`+`SITHE GOREWAY-G12`+`SITHE GOREWAY-G13`+`SITHE GOREWAY-G15`),n=n())
head(Dz_18)
```

```{r}
#plot_ly(Dz_18, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines') %>% layout(title='Goreway Generation 2018')
```



## Combining the data from 2013 to 2018 and making a single data file

```{r}
Dz_a13<-rbind(Dz_13,Dz_14,Dz_15,Dz_16,Dz_17,Dz_18)

str(Dz_a13)
```

### Date variable name from 2010 to 2012 are all caps .
### Changing as per “Date” which is from 2013 to 2018.
### 2010
```{r}
G10<-read_excel("GOC-2010.xlsx")
G10$DATE <- as.Date(G10$DATE, format = "%Y-%m-%d") # Changing to Date format
Dz_10<-G10 %>% group_by(DATE) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
colnames(Dz_10)[colnames(Dz_10)=="DATE"] <- "Date"
head(Dz_10)
```
### 2011

```{r}
G11<-read_excel("GOC-2011.xlsx")
G11$DATE <- as.Date(G11$DATE, format = "%Y-%m-%d") # Changing to Date format
Dz_11<-G11 %>% group_by(DATE) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
colnames(Dz_11)[colnames(Dz_11)=="DATE"] <- "Date"
head(Dz_11)
```
### 2012

```{r}
G12<-read_excel("GOC-2012.xlsx")
G12$DATE <- as.Date(G12$DATE, format = "%Y-%m-%d") # Changing to Date format
Dz_12<-G12 %>% group_by(DATE) %>% summarize(Goreway_Total=sum(`SITHE GOREWAY`),n=n())
colnames(Dz_12)[colnames(Dz_12)=="DATE"] <- "Date"
head(Dz_12)
```
### Combining the data from 2010 to 2012 and making a single data file 

```{r}
Dz_a10<-rbind(Dz_10,Dz_11,Dz_12)
head(Dz_a10)
```

### Combining the data from 2010 to 2018 and making a single data file

```{r}
Dz_y18<-rbind(Dz_a10,Dz_a13)
head(Dz_y18)
```

```{r}
dim(Dz_y18) # Dimensions of the data set
```

```{r}
#table(is.na(Dz_y18)) # Gives total number of missing values 
```
```{r}
#colSums(is.na(Dz_y18)) # checking variables in which missing values are present
```
```{r}
#write.table(Dz_y18,file="Output/Goreway_1.csv",sep=",",col.names=TRUE,row.names=F,append=FALSE)
```

```{r}
Gy_18<-na.omit(Dz_y18)
head(Gy_18,n=2)
```
```{r}
colSums(is.na(Gy_18)) # checking variables in which missing values are present
```

### Plotting the generation from 2010 till 2018

```{r}
library(ggplot2)

plot<-ggplot(Gy_18, aes(x=Date,y=Goreway_Total)) + geom_line()
plot
```
```{r}
is.data.frame(Gy_18)
```


```{r}
#library(plotly)
#plot_ly(Gy_18, x=~Date,y=~Goreway_Total)

#plot_ly(Gy_18, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines')

```

```{r}
Dz_y18$Year <- format(Dz_y18$Date, format = "%Y")
Dz_y18$Month_num <- format(Dz_y18$Date, format = "%m")
Dz_y18$Day <- format(Dz_y18$Date, format = "%d")

head(Dz_y18)
```
## Plotting the generation from 2010 till 2018

```{r}
library(ggplot2)

plot<-ggplot(Gy_18, aes(x=Date,y=Goreway_Total)) + geom_line()
plot
```

```{r}
is.data.frame(Gy_18)
```

```{r}
#library(plotly)
#plot_ly(Gy_18, x=~Date,y=~Goreway_Total)

#plot_ly(Gy_18, x=~Date) %>% add_trace(y=~Goreway_Total,mode='lines')
```
###Extract Year,Month and Day and store in separate columns

```{r}
Dz_y18$Year <- format(Dz_y18$Date, format = "%Y")
Dz_y18$Month_num <- format(Dz_y18$Date, format = "%m")
Dz_y18$Day <- format(Dz_y18$Date, format = "%d")

head(Dz_y18)
```

```{r}
Gy_18<-na.omit(Dz_y18)
head(Gy_18,n=2)
```

```{r}
p_year<-ggplot(Gy_18, aes(x=Year,y=Goreway_Total)) + geom_bar(stat="identity", fill="steelblue")
p_year
```


```{r}
Gy_18$Month_num<-as.factor(Gy_18$Month_num)
str(Gy_18)
```

```{r}
p_month<-ggplot(Gy_18, aes(x=Month_num,y=Goreway_Total)) + geom_bar(stat="identity", fill="steelblue")
p_month
```

